Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-16 talk/iwtc11/paper.tex
clarify and stress things

This scheme is quite powerful. It allows simple linear optimization passes to
perform loop-aware optimizations, such as loop-invariant code motion without
changing them at all. All that is needed is to peel off one iteration, then
apply simple one-pass optimizations and make sure that the necessary extra
arguments are inserted into the label of the loop itself and the jumps
afterwards. The peeling off of one iteration gives the optimization enough
context to remove operations from the peeled loop, because the optimization
detects that the operation was performed in the preamble already.

@@

\begin{itemize}
    \item \lstinline{new} creates a new object.
    \item \lstinline{get} reads an attribute of an object.
    \item \lstinline{set} writes to an attribute of an object.
    \item \lstinline{guard_class} is a precise type check. It typically precedes
    an (inlined) method call and is followed by the trace of the called method.
    \item \lstinline{guard_true} checks that a boolean is true.
\end{itemize}

>>>>

This scheme is quite powerful and generalizes to other optimizations than just
common subexpression elimination. It allows simple linear optimization passes to
perform loop-aware optimizations, such as loop-invariant code motion without
changing them at all. All that is needed is to peel off one iteration, then
apply simple one-pass optimizations and make sure that the necessary extra
arguments are inserted into the label of the loop itself and the jumps
afterwards. Giving the optimizations two iterations together
gives the optimization enough context to remove operations from the peeled loop,
because it detects that the operation was performed in the preamble already.

@@

\begin{itemize}
    \item \lstinline{new} creates a new object.
    \item \lstinline{get} reads an attribute of an object.
    \item \lstinline{set} writes to an attribute of an object.
    \item \lstinline{guard_class} is a precise type check. It typically precedes
    an (inlined) method call and is followed by the trace of the called method.
\end{itemize}
